%-------------------------
% Resume in Latex
% Author : Sravanthi Malepati
% Based off of: https://github.com/sravanthi-gsu/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Sravanthi Malepati} \\ \vspace{1pt}
    \small 408-310-3302 $|$ \href{mailto:x@x.com}{{smalepati1@student.gsu.edu}} $|$ 
    \href{https://linkedin.com/in/...}{{linkedin.com/in/sravanthi-malepati}} $|$     \href{http://www.sravanthimalepati.com/}{{www.sravanthimalepati.com}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia State University}{Atlanta, GA}
      {Master of Science in Computer Science; GPA: 3.76}{Jan. 2020 -- Dec. 2021}
     %\resumeItem{Course Work: Parallel algorithms, Semantic Web, Machine Learning, Advanced Software Engineering, Web Programming, Cryptography  }
    \resumeSubheading
      {RVR \& JC College of Engineering }{Andhra Pradesh, IN}
      {Bachelor of Technology in Computer Science; GPA: 3.7 (9.03/10.0)}{Aug. 2014 -- June. 2018}
      % \resumeItem{Course Work: Data Structures, Design and Analysis of Algorithms, Database Management Systems, Operating Systems, Data Mining}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Georgia State University}{Atlanta, GA}
      {Graduate Research \& Teaching Assistant}{Jan. 2020 -- Present}
      
      \resumeItemListStart
        \resumeItem{Working as a web developer and content manager, where my responsibilities include developing new components and building web pages using HTML/CSS, JavaScript, and PHP.}
        \resumeItem{Maintaining Smartworld 2021: The 7th IEEE Smart World Congress, Atlanta Website.}
        \resumeItem{Worked on analyzing publications data from Web of Science's website using Python and assist in developing statistical models for automation using R.}
        \resumeItem{Worked as a Graduate Teaching Assistant in designing and evaluating the data mining projects using Python Language for graduate and undergraduate students. Hosted weekly recitations and office hours to offer support to students.}
      \resumeItemListEnd
      
    \resumeSubheading
    {Assistant System Engineer, TATA Consultancy Services}{Bangalore, IN}
    {CyberArk Password Vault \& Microsoft Bit locker Administration and Monitoring}{June. 2018 -- Dec. 2019}
      \resumeItemListStart
        \resumeItem{On-boarded accounts using Password Upload Utility and created safe(vault) for different client stakeholders and updated management policy \& password policy and integrated using the \textbf{Password Vault} tool.}
        \resumeItem{Handled IT requests related to new account creations, resolved password synchronization failures, and executed SLA changes using the \textbf{ServiceNow} tool by performing a health check on CyberArk servers.}
        \resumeItem{Built custom \textbf{PowerShell} scripts on the client’s server to automate bulk accounts on-boarding.}
        \resumeItem{Managed the security protocol for more than 100K client devices using MBAM centralized console by maintaining encryption compliance over 99\%.}
        \resumeItem{Custom build MBAM server architecture with a disaster recovery mechanism as per the client’s requirements.}
        \resumeItem{Coordinated with the team \textbf{Data Migration} activity for the data stored in the devices from one data center to
another.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Software Developer Intern }{Visakhapatnam, IN}
      {Smart Village Project(University of California, Berkeley \& Govt. Of AP) }{May 2017 -- July 2017}
      
      \resumeItemListStart
        \resumeItem{Developed a static website for the project using essential web development tools (HTML, CSS \& JSS)}
        \resumeItem{Performed data analysis for survey data collected using Python libraries and developed a dynamic dashboard to understand the village’s demographics.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
          \resumeProjectHeading
       {\textbf{ADHD Classification using Neural Networks}}{\textbf {LSTM, niLearn, NumPy, Keras}}
        
            \resumeItem{A classification significance of rs-fMRI Data to build Neural Network Models using python libraries.}
         
        \resumeProjectHeading
          {\textbf{Secure Chat Room Application}} {\textbf {Java API, Servlets, KeyStore’s}}
          
            \resumeItem{Developed a secure chatroom application with authentication and privacy for message transfer.}
          
      \resumeProjectHeading
          {\textbf{Continuous Top-k Monitoring on Document Streams}} 
          {\textbf{Java (Spring Boot), Rest API, JSP}}
            \resumeItem{Designed and created a program to support large numbers of users and high stream rates while refreshing the important keywords instantaneously using ID-Ordering techniques for query processing.}
          
          \resumeProjectHeading
          {\textbf{Online Movie Ticket Management}} {\textbf{HTML/CSS, JavaScript, MySQL, XAMPP server, Bootstrap}}
            \resumeItem{Developed a web application to reserve movie tickets and maintain the customer’s records using web development tools.}
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Languages}{: Python, Java, C/C++, J2EE, HTML/CSS, JavaScript, SQL (MSSQL, MySQL)} \\
     \textbf{Technologies}{: Angular, Bootstrap, Servlets, JDBC, RESTful Webservices, Spring MVC, XML, Android} \\
     \textbf{Tools}{: Microsoft Office, Service Now, Git, JIRA, Visual Studio, Eclipse, Tableau, Jupyter} \\
     %\textbf{Technologies}{: Python, Java, C/C++, J2EE, HTML/CSS, JavaScript, SQL (MySQL), Hadoop, Big Data, Apache Spark, React, Node.js, Android, WordPress, JDBC, RESTful Webservices, Bootstrap, Microsoft Office, Git, Visual Studio, Eclipse, Tableau, Jupyter } \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
